
% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{paralist}

\newcommand{\parsp}{\vspace{-0.7\baselineskip}}
\newcommand{\additemindent}{\addtolength{\itemindent}{1em}}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{10in} % increase text height to fit on 1-page 

\begin{document} 

\name{Jingyun Bian\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf ADDRESS\\Unit 1902, 4070 Confederation Pkwy\\Mississauga, ON. L5B 0E9\\}
%\address{\bf Contact\\ cell: (519) 721-7328 \\ email: rayleigh0328@gmail.com\\}
\address{\bf CONTACT\\ Cell: (519) 721 - 7328 \\ \href{mailto:j4bian@uwaterloo.ca}{rayleigh0328{\fontfamily{ptm}\selectfont @}gmail.com} \\}

\begin{resume}

%=======================================================================================
\parsp
\section{SUMMARY OF QUALIFICATION}
	\begin{asparaitem}
		\item 	Proficient in Java, Maven, Bash, Git, Vim, C/C$^{++}$, Makefile, \LaTeX, Pascal, Matlab, Python, PHP, Javascript, HTML, CSS, SQL, Hadoop(Oozie, Yarn, spark, Zookeeper, Kafka, Impala, Hive, Hdfs), Jenkins, Redis, Elasticsearch.
		\item 	Knowledge about information theory, machine learning.
		\item 	Communication and problem solving skills developed through researching, teaching and working.
	\end{asparaitem}
%=======================================================================================	


%=======================================================================================
\parsp
\section{EDUCATION}
	\textbf{M.A.Sc, University of Waterloo, Waterloo, ON} \hfill \emph{Sep. 2014- Sep. 2016
	}
	\begin{asparaitem}[$\circ$]
		\additemindent
		\item Electrical and Computer Engineering, GPA 86.6/100
		\item Concentrate on Communications and Information Systems
		% \item Supervisor: Prof. En-hui Yang
  	\end{asparaitem}

  	\vspace{-0.7\baselineskip}

	\textbf{B.Sc, Nanjing University, Nanjing, Jiangsu, China} \hfill \emph{Sep. 2010 - Jul. 2014}
	\begin{asparaitem}[$\circ$]
		\additemindent 
		\item Computer Science, Member of ``Top Notch Plan'', GPA 4.13/5
	\end{asparaitem}
%=======================================================================================



%=======================================================================================
\parsp
\section{EXPERIENCE}
\begin{asparaitem}
	\item \textbf{Software engineer in test, Centro,} \hfill \emph{Nov. 2016 - Present}
		\begin{asparaitem}
			\additemindent
			\item Design and implement automated tests for multiple teams and projects
			\begin{asparaitem}
				\additemindent
				\item \emph{Big Data}: E2E, batch-aggregation, kafka-ingest, scrubber, evpump-dimension, discrepancy-finder, audit-stats, table schemas
				\item \emph{API}: rule-based-optimization, bid-multiplier
				\item \emph{Backend}: rule-based-optimization, inventory-planner, stats consumer 
				\item \emph{Buisiness Intelligence}: change-capture, org-pipeline, historical-dimensions, schemas
			\end{asparaitem}
		\end{asparaitem}

	\item \textbf{Research Assistant}, ECE, University of Waterloo, \hfill \emph{Sep. 2014 - Oct. 2016}
		\begin{asparaitem}
			\additemindent
			\item Research Project: Bipartite Grammar-Based Representations of Large Sparse Binary Matrices.
			\item Supervisor: Prof. En-hui Yang. 
		\end{asparaitem}

	\item Teaching Assistant, ECE, University of Waterloo, \hfill \emph{Sep. 2014 - Aug. 2016}
		\begin{asparaitem}
			\additemindent
			\item Courses: Fundamentals of Programming, Algorithms and Data Structures, Compilers
		\end{asparaitem}

	\item Undergraduate Research Assistant, CS, Nanjing University, \hfill \emph{Sep. 2013 - Sep. 2014}
		\begin{asparaitem}
			\additemindent
			\item Project: Online-judge Based Fault Localization System, supervised by: Lin Chen.
		\end{asparaitem}
	\item Co-funder of Alibaba Technology Association of Nanjing University, \hfill \emph{Sep. 2013 - Sep. 2014}
	% \item Minister of academic section of CS department's student union, Nanjing University, 2010 - 2011	
\end{asparaitem}

%=======================================================================================


%=======================================================================================
\parsp
\section{PUBLICATION AND CONTEST}
	\begin{asparaitem}
		\item En-hui Yang, Jingyun Bian, 
		\textbf{``Bipartite Grammar-Based Representations of Large Sparse Binary Matrices: Framework and Transforms''}, 
		\emph{The International Symposium on Information Theory and Its Applications(ISITA)}, 
		Monterey, California, 
		2016.
		\item \textbf{ACM/ICPC} Asian Regional Silver Medal (2013 Changsha), Four Bronze Medals (2012 Changchun, 2012 Jinhua, 2011 Fuzhou, and 2011 Beijing)
		% \item $4$ ACM/ICPC Asian Regional Bronze Medals: 2012 Changchun, 2012 Jinhua, 2011 Fuzhou, and 2011 Beijing.
	\end{asparaitem}
%=======================================================================================


%=======================================================================================
\parsp
\section{PROJECT}
\begin{asparaenum}

	% \item Designed and implemented testing projects for projects stated in the EXPERIENCE section.

	\item Implementation of Context-dependent $2$-D Multi-level Pattern Matching Code, Course Project of \emph{Data Compression}, \hfill \emph{Winter 2015}

	\item Security Analysis and Randomness Test for Lightweight Block Cipher Simon, Course Project of \emph{Computer Network Security}, \hfill \emph{Winter 2015}

	\item Emotion Analysis of Tweets, Course Project of \emph{Topics in Computer Software}, \hfill \emph{Fall 2014}
		\begin{asparaitem}
			\additemindent
			\item Utilized Python NLTK package and PCA for preprocessing and 
			\item Applied SVM, C$4.5$, Bayes and Neural Network to compare the classification accuracy.
		\end{asparaitem}

	\item GRE Vocabulary Memorizing System, \emph{Bachelor Dissertation Project}, \hfill \emph{2014}
		\begin{asparaitem}
			\additemindent
			\item Applied XAMPP, Bootstrap to build the website.
			\item Integrated with wechat API to provide in-App access.
		\end{asparaitem}

	\item Simple graphic system, Course Project of \emph{Introduction to graphics}, \hfill \emph{2013}
		\begin{asparaitem}
			\additemindent
			\item Implemented basic graphic functions using OpenGL in C++ and built a simple GUI. 
		\end{asparaitem}

	
 	\item User behavior classification based on cell-phone sensor data, Course Project of \emph{Data Mining}, \hfill \emph{2013}
 		\begin{asparaitem}
			\additemindent
			\item Used WEKA to do data cleaning and classification. 
		\end{asparaitem}

\end{asparaenum}





%=======================================================================================
% \parsp
% \section{EXTRACURRICULAR ACTIVITIES}
% \begin{asparaitem}
% \item Minister of academic section in student union of CS department in NJU
% \item Co-funder of Alibaba Technology Association of Nanjing University
% \end{asparaitem}
%=======================================================================================

\end{resume}
\end{document}